---
title: "ToothGrowth Data Analysis"
author: "liwenlong"
output: pdf_document
---

#Overview
In this report, I will perform some basic explortary data analyses on the ToothGrowth data, And compare tooth growth by supp and dose.
```{r lib, message=FALSE}
library(dplyr)
library(datasets)
library(ggplot2)
```

#Read data
- View the structure of the data
```{r readData}
#convert the dose from num to factor
ToothGrowth$dose <-as.factor(ToothGrowth$dose)
str(ToothGrowth)
table(ToothGrowth$supp,ToothGrowth$dose)
```
We have sixty records group by supp(QJ,VC) and dose (0.5,1,2), and for each group there is 10 records.

- Explor the data by dose and supp
```{r dataExplor,fig.width=3,fig.height=3}
#summary by supp
ggplot(ToothGrowth,aes(x=supp,y=len))+
        geom_boxplot(fill="grey")+
        ggtitle("Tooth Length by Supp")

#summary by dose
ggplot(ToothGrowth,aes(x=dose,y=len))+
        geom_boxplot(fill="grey")+
        ggtitle("Tooth Length by Dose")
```

# Tooth length compare by Supp
- Assumption is there is no difference between two Supp group(They have the same mean value).
- I didn't read the description of this dataset, but from the definition of the problem, it doesn't tell us the data is paired or they have the same variance. So i will set {paired = F,var.equal = F}
```{r bySupp}
testBySupp <- t.test(subset(ToothGrowth$len,ToothGrowth$supp=="OJ"),
       subset(ToothGrowth$len,ToothGrowth$supp=="VC"),
       var.equal = F,
       paired = F)
c(testBySupp$conf,testBySupp$p.value)
```
- The 95 percent confdence interval[**`r testBySupp$conf.int`**] contains 0. And the P-Value [**`r testBySupp$p.value`**] is greater than 0.05.
- So we do not have conclusive evidence to show that OJ has a better effect on tooth growth and failed to reject the null hypothesis.
- Actually I also tried other params for the test,setting {var.equal=T} doesn't make any difference, while setting {paired = T} will lead to a totally different result). 

# Tooth length compare by Dose
- The Null Hypothesis is the mean value are the same for different dose group.
- User {paired = F,var.equal = F} for the test, same reason as above. 
```{r by Dose}
test1<-t.test(subset(ToothGrowth$len,ToothGrowth$dose==1),
       subset(ToothGrowth$len,ToothGrowth$dose==.5), 
       var.equal = F,paired = T)
test2<-t.test(subset(ToothGrowth$len,ToothGrowth$dose==2),
       subset(ToothGrowth$len,ToothGrowth$dose==1),
       var.equal = F,paired = T)
c(test1$conf,test1$p.value)
c(test2$conf,test2$p.value)
```
- From both tests, the 95-percent-interval is above 0 with p-value < .05 which provides statistical evidence that higher Dose DOES have positive impact on tooth length.
- Setting [var.equal = T] shows the same result, while setting {paired = T} leads to a slightly different result, but the conclusion is still the same. 
